Effect of Sociological Factors on Visual Statistical Inference

### 2024-12-31 wiley_paper/wiley_paper.Rnw
Add files via upload

\if0\blindDoc
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\bf \LARGE Human Factors Influencing Visual Statistical Inference}
\end{center}
  \medskip
} \fi

@@

Visual statistical inference determines the significance of patterns found in data exploration through graphics. It involves human observers inspecting a lineup of plots, with one real data plot randomly placed among decoys. Each observer's cognitive skills and judiciousness can influence results. The effectiveness of this method, measured by power, depends on combining evaluations from multiple observers. Factors influencing power include observer demographics, visual skills, experience, the sample of null plots, plot position, and signal strength. This paper examines these factors through studies using Amazon's Mechanical Turk, finding individual skills vary but demographics have little impact. Learning increases speed but not accuracy, and plot position doesn’t affect results.

@@

\if1\blindDoc
{
%------------------------------------------------------------------------------------
\paragraph{Acknowledgments}
%------------------------------------------------------------------------------------
This work was funded in part by National Science Foundation grant DMS 1007697. All studies were conducted with approval from the Institutional Review Board IRB 10-347.
} \fi

>>>>

\if0\blindDoc
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\bf \LARGE Effect of Sociological Factors on Visual Statistical Inference}
\end{center}
  \medskip
} \fi

@@

Visual statistical inference determines the significance of patterns found in data exploration through graphics. It involves human observers inspecting a lineup of plots, with one real data plot randomly placed among decoys. Each observer's cognitive skills and judiciousness can influence results. The effectiveness of this method, measured by power, depends on combining evaluations from multiple observers. Factors influencing power include observer demographics, visual skills, experience, the sample of null plots, and signal strength. This paper examines these factors through studies using Amazon's Mechanical Turk, finding individual skills vary but demographics have little impact. Learning increases speed but not accuracy.

@@

\section{Funding Information}
This work was funded in part by National Science Foundation grant DMS 1007697. All studies were conducted with approval from the Institutional Review Board IRB 10-347.

% \if1\blindDoc
% {
% %------------------------------------------------------------------------------------
% \paragraph{Acknowledgments}
% %------------------------------------------------------------------------------------
% This work was funded in part by National Science Foundation grant DMS 1007697. All studies were conducted with approval from the Institutional Review Board IRB 10-347.
% } \fi
